Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-07-25 emsoft-2019/camera_ready/Cont_Syn.tex
polishing the text

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily,escapeinside={<@}{@>}]
 model = input() 
 $\Delta$ = input()
 $\varepsilon_{Q}$ = input()
 assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
 $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@\Mahmoud{//width of the tube}@>

@@

Unlike the initial $\Delta$, $\varepsilon_Q$ needs to be strictly positive (line 4)
for mixed-precision tuning tools to work correctly.
Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
which will be used to bound the error due to selecting the wrong region
($\varepsilon_{A/D}$ is a constant parameter dependent on the specifics of the
converter).

@@

>>>>

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily,escapeinside={<@}{@>}]
 model = input() 
 $\Delta$ = input()
 $\varepsilon_{Q}$ = input()
 assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
 $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@$\quad$//\,\,width of the tube@>

@@

Unlike the initial $\Delta$, $\varepsilon_Q$ needs to be strictly positive (line 4)
for mixed-precision tuning tools to work correctly. \Mahmoudd{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up to $10^{-2}$. Increasing $\varepsilon_Q$ leads into more memory save over $H$ and $K$ while requiring more precision for $F$ and $G$. Of course, too large values for $\varepsilon_Q$ can result in failure of the RMPC design. However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
which will be used to bound the error due to selecting the wrong region
($\varepsilon_{A/D}$ is a constant parameter dependent on the specifics of the
converter).

@@

\smallskip
\noindent
\Mahmoudd{
\textbf{Termination of the algorithm.}
From a theoretical point of view, the error due to a wrong region selection does not necessarily converge since each new designed controller may differ from the previous ones. Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated. However, by rewriting \autoref{eq:RMPC_prob}, we have
\begin{align*}
\nu_0(x_0, \Delta),\ldots&,\nu_{N-1}(x_0,\Delta)=\\
argmin & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
\quad  \text{s.t.} \quad & x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\}.
%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
\end{align*}
Assuming the optimization has a unique solution for every $\Delta$, 
one may use the results on continuity of the $argmin$ function to compute an upper bound on the Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$. The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection. This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence. From an experimental point of view, our observations show that using a reasonable $\varepsilon_{SAFE}$, convergence always reached after only a few iterations.}

\smallskip
\noindent
\Mahmoudd{
\textbf{Computational complexity.} It is shown in \cite{Alessio2009} that the number of regions $P$ in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
%In theory, one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.
Assuming that each region has at most $\bar n_f$ hyperplanes, computation of the incorrect region selection error requires at most $i\times\bar n_f\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence. In our experiments, the computation of the incorrect region selection error takes only a few minutes for our largest tested benchmarks. %\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}} 		
\\
The complexity of the precision tuning is linear with respect to the number of regions and hyperplanes. So, $(P+\bar n_f\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
In each encoding, the uniform-precision detection takes linear number of steps before convergence. It starts from 1-bit and increases the precision one by one until the first valid configuration. The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with $n$ being the number of variables.}

### 2019-07-25 emsoft-2019/camera_ready/Error_Analysis.tex
polishing the text

\begin{equation*}
\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
\end{equation*}
where $\varepsilon$ captures the uncertainty in computing the correct region.
%
The width of the tube $\varepsilon$ is due to two sources of errors:
analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
bounds in memory $\varepsilon_{Q}$:
\begin{equation}\label{eq:epsilontot}
  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}

@@

@@

While our actual synthesis algorithm (\autoref{sec:Controller_Synthesis}) does
not compute the errors $\varepsilon_Q$ and $err(v_{i})_{p}$ explicitly, the
error verification is used internally by Daisy to determine a suitable precision
$p$ and can also be called explicitly without the precision optimization.

\begin{comment}
\textcolor{red}{Sadegh: This is long comment on the content of this section. I cannot figure out how this line of reasoning is mapped to the implementation. We can discard my comment given that we are close to the deadline.}

>>>>

\begin{equation*}
\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
\end{equation*}
where $\varepsilon$ captures the uncertainty in computing the correct region.
%
The width of the tube $\varepsilon$ is due to two sources of errors:
analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
bounds in memory $\varepsilon_{Q}$:
\begin{equation}\label{eq:epsilontot}
  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}

@@

 %\Mahmoudd{ 
 %\begin{remark}
 %	Our formulation is general enough to take the effect of measurement/process noise into account. More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources. However, this is not subject of study of the current paper. Moreover, to cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}. Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$. For reasonable values of $\Delta$, in principle RMPC design should work successfully. Further, it should be noticed that the rest of analysis (over MATLAB and Daisy) do not rely on the LTI property of the under study system and could be adjusted for other families of controllers. However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
 %	\end{remark}}

@@

While our actual synthesis algorithm (\autoref{sec:Controller_Synthesis}) does
not compute the errors $\varepsilon_Q$ and $err(v_{i})_{p}$ explicitly, the
error verification is used internally by Daisy to determine a suitable precision
$p$ and can also be called explicitly without the precision optimization. \Mahmoudd{To encourage reproducible research, our implementation is made available online.\footnote{\url{https://github.com/rospoly/rmpc-daisy}}}
\Mahmoudd{\begin{remark}
	Note that we use MATLAB and Daisy solely for offline computations. The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems. Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.
\end{remark}}
\begin{comment}
\textcolor{red}{Sadegh: This is long comment on the content of this section. I cannot figure out how this line of reasoning is mapped to the implementation. We can discard my comment given that we are close to the deadline.}

### 2019-07-25 emsoft-2019/camera_ready/Motiv.tex
polishing the text

		%\begin{center}
		%\hspace*{\fill} 
		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set \Mahmoud{$\mathcal W_{\Delta}$}};
		\Mahmoud{\node [block1,below = 0.8cm of RMPC] (highprec) {High-precision controller (\autoref{eq:affine_map})};}
		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
		\node [block3,below=.8cm of highprec,
		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
		\node [block2, right=1.3cm of decide,
		node distance=1cm] (delta) {\Mahmoud{ $\Delta=e+\varepsilon_{SAFE}$}};
		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
		\node at (9,-.25) {$e$};

@@

For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
We use Matlab to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
%
The output of robust EMPC given by Matlab decomposes the control domain into a
finite number of polyhedral domains together with an affine map for each domain. 
At each time step, the state vector $x_k$ is read (or estimated) and based on the domain
that it belongs to, the corresponding control output is computed. 
However, the polyhedral regions are implemented in finite precision so that
it is possible that due to quantization errors the domain is selected incorrectly, and therefore
a different affine map is computed for the control.
We refer to the resulting error as \emph{incorrect region selection} error.
% However, due to error by fixed-point implementation, it is possible that the domain is selected
% incorrectly. This causes an error term which we refer to it as incorrect region
% selection error.
In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount \Mahmoud{$\varepsilon_{SAFE}=0.031$} to
$\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.

@@

Next, we use the precision tuning tool Daisy \cite{Daisy} to provide a mixed-precision 
implementation for all the parameters which satisfies the error bound $\Delta_1  - e = 0.05 - 0.019 = 0.031$.
The mixed-precision implementation returned by Daisy requires $6084$ bits.
Thus, \Mahmoud{for this introductory example,} the mixed-precision implementation takes about $10\%$ less memory compared 
to the smallest uniform precision implementation that respects $\Delta_1$,
and about $57\%$ less memory than an implementation that uniformly uses
32 bits.

>>>>

		%\begin{center}
		%\hspace*{\fill} 
		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
		\node [block1,below = 0.8cm of RMPC] (highprec) {\Mahmoud{High-precision controller (\autoref{eq:affine_map})}};
		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
		\node [block3,below=.8cm of highprec,
		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
		\node [block2, right=1.3cm of decide,
		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
		\node at (9,-.25) {$e$};

@@

For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
We use Matlab to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
%
The output of robust EMPC given by Matlab decomposes the control domain into a
finite number of polyhedral domains together with an affine map for each domain. 
At each time step, the state vector $x_k$ is read (or estimated) and based on the domain
that it belongs to, the corresponding control output is computed. 
However, the polyhedral regions are implemented in finite precision so that
it is possible that due to quantization errors the domain is selected incorrectly, and therefore
a different affine map is computed for the control.
We refer to the resulting error as \emph{incorrect region selection} error.
% However, due to error by fixed-point implementation, it is possible that the domain is selected
% incorrectly. This causes an error term which we refer to it as incorrect region
% selection error.
In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount $\varepsilon_{SAFE}=0.031$ to
$\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.

@@

Next, we use the precision tuning tool Daisy \cite{Daisy} to provide a mixed-precision 
implementation for all the parameters which satisfies the error bound $\Delta_1  - e = 0.05 - 0.019 = 0.031$.
The mixed-precision implementation returned by Daisy requires $6084$ bits.
Thus, for this introductory example, the mixed-precision implementation takes about $10\%$ less memory compared 
to the smallest uniform precision implementation that respects $\Delta_1$,
and about $57\%$ less memory than an implementation that uniformly uses
32 bits.

### 2019-07-25 emsoft-2019/camera_ready/RMPC_Daisy.tex
colors-->blue
polishing the text

\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider the class of linear time-invariant (LTI) systems characterized by the difference equation
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k,\quad  k=0,1,2,\ldots
\end{equation}
where $x\in \reals^{n\times 1}$ is the state, $u\in \reals^{m\times 1}$ is the control input and $w\in \reals^{d\times 1}$ is the disturbance. Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$  capture respectively the effects of current state, input and disturbance on the next state. We assume the disturbance $w$ belongs to a set $\Mahmoud{\mathcal{W}_{\Delta}}$ where $\Mahmoud{\mathcal{W}_{\Delta}}$ is a polyhedral set \Mahmoud{defined by \autoref{eq:W_delta}}.
In this paper, we focus on the robust formulation of MPC which at each time step
minimizes the worst-case value of an objective function with respect to the
disturbances over the control inputs. We assume the objective function is
quadratic with respect to the states and inputs.
We assume a linear translation on the input with the form
$$u_k=\mu x_k+v_k$$
and synthesize $v_k$ instead of $u_k$. This choice reduces the 
conservativeness of the optimization and enlarges the set of feasible input
trajectories. The matrix $\mu$ is selected such that some desired property is satisfied under suitable assumptions on the system, e.g., stability if the pair $(A,B)$ is stabilizable.

%\eva{I don't understand the above sentence. Maybe split into several sentences? Where does $u_k$ come from (the sentence right now says you assume $u_k$)?}
%The modifed state evolution of the system will be $x_{k+1}=\bar Ax_k+Bv_k+Ew_k$ with $\bar A := A +BK$.
% and $v_k=\kappa(x_k)$ denotes the output of model predictive controller.  
The constrained optimization at each time step is of the form
\begin{align}
\label{eq:RMPC_prob}
J^{\ast}(x_0)=&\min_{v_0,\cdots,v_{N-1}} \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
\text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\Mahmoud{\mathcal{W}_{\Delta}},\,\,\forall i\in\{0,1,\cdots,N\},
%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
\end{align}
%\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
%
where $\mathcal U$ and $\mathcal X$ are polyhedral sets denoting the feasible
sets of inputs and states. Positive definite matrices $Q\in\reals^{n\times n}$ and
$Q_F\in\reals^{n\times n}$ indicate weights on the states. $R\in\reals^{m\times m}$ is
positive semidefinite and indicates a weight on the input in the objective function. $N$ denotes the length of the prediction horizon.
%\eva{What are $Q, Q_F, R$ and where do they come from?}

\begin{theorem}[\cite{delaPea:2005}]
\label{thm:EMPC}
The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution. Furthermore, for the case that $R>0$, the controller is $u_k = \mu x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
\label{eq:affine_map}
\kappa(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
\end{theorem}
The essential idea behind this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
%\begin{align}
%	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
%	&s.t.\quad JU_N\leq s+Dx_0
%\end{align} 
\begin{align}
\label{eq:multi_param_prog}
J^{\ast}(x_0)=\min_{z,\gamma}& \left[x_0^TYx_0+\frac{1}{2}z^THz+\gamma\right]\\
\text{s.t.} \quad &G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
&G_cz\leq W_c+S_cx_0\nonumber
\end{align}
where $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables, and $Y$, $H$, $G_m$, $G_c$, $S_m$, $S_c$, $W_m$, $W_c$, and $g_m$ 
are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).

@@

The implementation of the controller stores the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$. 
At each time step $k$, the current state $x_k$ is used to detect the polyhedral region 
such that $H_i x_k\le K_i$. Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 
The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).

>>>>

\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider the class of linear time-invariant (LTI) systems characterized by the difference equation
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k,\quad  k=0,1,2,\ldots
\end{equation}
where $x\in \reals^{n\times 1}$ is the state, $u\in \reals^{m\times 1}$ is the control input and $w\in \reals^{d\times 1}$ is the disturbance. Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$  capture respectively the effects of current state, input and disturbance on the next state. We assume the disturbance $w$ belongs to a set $\mathcal{W}_{\Delta}$ where $\mathcal{W}_{\Delta}$ is a polyhedral set defined in \autoref{eq:W_delta}.
In this paper, we focus on the robust formulation of MPC which at each time step
minimizes the worst-case value of an objective function with respect to the
disturbances over the control inputs. We assume the objective function is
quadratic with respect to the states and inputs.
We assume a linear translation on the input with the form
$$u_k=\mu x_k+v_k$$
and synthesize $v_k$ instead of $u_k$. This choice reduces the 
conservativeness of the optimization and enlarges the set of feasible input
trajectories. The matrix $\mu$ is selected such that some desired property is satisfied under suitable assumptions on the system, e.g., stability if the pair $(A,B)$ is stabilizable.

%\eva{I don't understand the above sentence. Maybe split into several sentences? Where does $u_k$ come from (the sentence right now says you assume $u_k$)?}
%The modifed state evolution of the system will be $x_{k+1}=\bar Ax_k+Bv_k+Ew_k$ with $\bar A := A +BK$.
% and $v_k=\kappa(x_k)$ denotes the output of model predictive controller.  
The constrained optimization at each time step is of the form
\begin{align}
\label{eq:RMPC_prob}
J^{\ast}(x_0)=&\min_{v_0,\cdots,v_{N-1}} \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
\text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\},
%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
\end{align}
%\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
%
where $\mathcal U$ and $\mathcal X$ are polyhedral sets denoting the feasible
sets of inputs and states. Positive definite matrices $Q\in\reals^{n\times n}$ and
$Q_F\in\reals^{n\times n}$ indicate weights on the states. $R\in\reals^{m\times m}$ is
positive semidefinite and indicates a weight on the input in the objective function. $N$ denotes the length of the prediction horizon.
%\eva{What are $Q, Q_F, R$ and where do they come from?}

\begin{theorem}[\cite{delaPea:2005}]
\label{thm:EMPC}
The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution. Furthermore, for the case that $R>0$, the controller is $u_k = \mu x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
\label{eq:affine_map}
\kappa(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$.
\end{theorem}

The proof of this theorem can be found in \cite{delaPea:2005}. The essential idea behind the theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
%\begin{align}
%	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
%	&s.t.\quad JU_N\leq s+Dx_0
%\end{align} 
\begin{align}
\label{eq:multi_param_prog}
J^{\ast}(x_0)=\min_{z,\gamma}& \left[x_0^TYx_0+\frac{1}{2}z^THz+\gamma\right]\\
\text{s.t.} \quad &G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
&G_cz\leq W_c+S_cx_0\nonumber
\end{align}
where $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables, and $Y$, $H$, $G_m$, $G_c$, $S_m$, $S_c$, $W_m$, $W_c$, and $g_m$ 
are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).

@@

The implementation of the controller stores matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$. 
At each time step $k$, the current state $x_k$ is used to detect the polyhedral region 
such that $H_i x_k\le K_i$. Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 
The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
\Mahmoudd{
\begin{remark}
	The total time to evaluate the PWA function in \autoref{eq:affine_map} for a given $x_k$ consists of two steps: (a) selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$ and (b) evaluating the corresponding affine map $F_i x_k +G_i$.
	Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step. Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient. More efficiency can be achieved by leveraging binary search tree structures (e.g. \cite{Mnnigmann:2011}).\\
	In general, explicit MPC is well-known for its high-speed implementation over embedded systems with low computational power. The authors in \cite{Johansen:2007} show that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuits (ASIC) with about $20000$ gates, leading to computation times in the order of $1\mu s$. It is shown in \cite{Bemporad:2006} that for typical problems evaluating the explicit MPC takes significantly shorter time in comparison to solving on-line quadratic programs.
\end{remark}}

\Mahmoudd{ 
 \begin{remark}
 It should be noticed that EMPC is a class of controllers specifically proposed for linear time invariant (LTI) systems. To cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}. Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$. For reasonable values of $\Delta$, in principle RMPC design should work successfully. Further, it should be noticed that the rest of analysis in the sequel (over MATLAB and Daisy) do not rely on the LTI property of the system under study and could be adjusted for other families of controllers.
 %However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
\end{remark}}

### 2019-07-25 emsoft-2019/camera_ready/conclusion.tex
camera_ready folder is added
polishing the text

\section{Conclusion}

We have described an automatic technique to tune an explicit MPC
controller that implements the controller in mixed-precision fixed-point arithmetic
while ensuring that the resulting loss of precision does not invalidate the
constraints of the original control problem.
Our technique models potential fixed-point imprecision explicitly as a disturbance
term, and uses robust explicit MPC to design a controller.
A static error analysis and a mixed-precision tuning tool is then 
used to find an efficient implementation of the controller function.
The implementation maintains the numerical error to within
the disturbance bounds used by the robust controller.
In experiments, we show that our technique can yield significant savings in memory,
ranging up to 20\%. 
In addition, the static analysis scales to controllers with hundreds of regions. \Mahmoud{All in all, using our proposed method, model predictive control under input and state constraints can be achieved while the memory footprint is minimized. By leveraging our method, memory requirement for implementation of explicit MPCs over the industrial embedded systems reduces. One exciting direction for future work would be to investigate effect of stochastic noises on the proposed design methodology.}

>>>>

% !TEX root = main.tex
\section{Conclusion}

We have described an automatic technique to tune an explicit MPC
controller that implements the controller in mixed-precision fixed-point arithmetic
while ensuring that the resulting loss of precision does not invalidate the
constraints of the original control problem.
Our technique models potential fixed-point imprecision explicitly as a disturbance
term, and uses robust explicit MPC to design a controller.
A static error analysis and a mixed-precision tuning tool is then 
used to find an efficient implementation of the controller function.
The implementation maintains the numerical error to within
the disturbance bounds used by the robust controller.
In experiments, we show that our technique can yield significant savings in memory,
ranging up to 20\%. 
In addition, the static analysis scales to controllers with hundreds of regions.\\
One exciting direction for future work would be to investigate the effect of stochastic disturbances on the proposed methodology and find a scheme to reduce statistically the memory footprint of the controller implementation.

%\Mahmoud{All in all, using our proposed method, model predictive control under input and state constraints can be achieved while the memory footprint is minimized. By using our method, memory requirement for implementation of explicit MPCs over the industrial embedded systems reduces. One exciting direction for future work would be to investigate effect of stochastic noises on the proposed design methodology.}
